---
title: "Predictions"
output: html_document
date: "2024-10-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stats)
library(ggplot2)
library(dplyr)
library(lubridate)
library(readr)
```

# NOT DOING THIS NOW, BUT JUST WANTED TO KEEP IN CASE 
```{r}
# SEE ABOVE!!!
# data <- read.csv("~/Desktop/predictions.csv")
# colnames(data)
# file:///Users/andrewcramer/Downloads/31120080_qre.pdf (SEE 314) ((p45-47, 57))
#Q15: Registered voter
#Q19: Senator vote
#Q20: Governor vote
#Q41: Increasing income taxes on people making over one million dollars per years
#Q42: Require background checks for gun purchases at gun shows or other private sales.
#Q49: Increase govt regulation of businesses that produce a great deal of greenhouse emissions linked to climate change
#Q72: Abortion view
#Q74: Concern that immigration poses a threat to the United States
#KS4: Over the past few years, Black Americans have gotten less than they deserve
#Q85 (p69): Highest level of school 
#Q86: Annual income
#Q87: Party
```

# [CES2022 data](https://gdcc.github.io/dataverse-previewers/previewers/v1.4/PDFPreview.html?callback=aHR0cHM6Ly9kYXRhdmVyc2UuaGFydmFyZC5lZHUvYXBpL3YxL2ZpbGVzLzczNTkyNTQvbWV0YWRhdGEvMTAzODA2ODcvdG9vbHBhcmFtcy84MA==&locale=en)

```{r}
data <- read.csv("~/Desktop/CCES22_Common_OUTPUT_vv_small.csv")
#CC22_327grid: Healthcare
#CC22_330grid: Guns
#CC22_331grid: Immigration
#CC22_332grid: Abortion
#CC22_333: Climate
#CC22_333grid: Environment
#CC22_334grid: Policing policies
#pid7

data <- data[, c("gender4", "educ", "race", "votereg", "pid7", 
                 "CC22_327a", "CC22_327b", "CC22_327c", "CC22_327d",
                 "CC22_330a", "CC22_330b", "CC22_330c", "CC22_330d", 
                 "CC22_330e", "CC22_330f", "CC22_331a", "CC22_331b",          
                 "CC22_331c", "CC22_331d", "CC22_332a", "CC22_332b", 
                 "CC22_332c", "CC22_332d", "CC22_332e", "CC22_332f", 
                 "CC22_333", "CC22_333a", "CC22_333b", "CC22_333c",          
                 "CC22_333d", "CC22_333e", "CC22_334a", "CC22_334b", 
                 "CC22_334c", "CC22_334d", "CC22_334e", "CC22_334f", 
                 "CC22_334g", "CC22_334h", "CC22_340a", "CC22_340b",
                 "CC22_340c", "CC22_340d", "CC22_340e", "CC22_340f", 
                 "CC22_340g", "CC22_340h", "CC22_340i", "CC22_340j", 
                 "CC22_340k", "CC22_340l", "CC22_340m", "CC22_340n")]


```
# Clean up dataset
## Create issue scales
Percent of questions on each issue dimension where choose liberal view

### Healthcare
```{r}
# Initialize to 0
data$health <- 0
#A: Expand Medicare
data <- data %>%
  mutate(health = if_else(CC22_327a == 1, health + 1, health))

#B: Government negotiate lower prices
data <- data %>%
  mutate(health = if_else(CC22_327b == 1, health + 1, health))

#C: Repeal Obamacare
data <- data %>%
  mutate(health = if_else(CC22_327c == 2, health + 1, health))

#D: Import prescriptions
data <- data %>%
  mutate(health = if_else(CC22_327d == 1, health + 1, health))

#Average
data$health <- data$health / 4.0

table(data$health)
```
### Gun control
```{r}
# Initialize to 0
data$guns <- 0
#A: Prohibit state from publishing gun registry
data <- data %>%
  mutate(guns = if_else(CC22_330a == 2, guns + 1, guns))

#B: Ban assault rifles
data <- data %>%
  mutate(guns = if_else(CC22_330b == 1, guns + 1, guns))

#C: Easier to obtain concealed-carry permit
data <- data %>%
  mutate(guns = if_else(CC22_330c == 2, guns + 1, guns))

#D: Funding to encourage states to take guns away from self-threats
data <- data %>%
  mutate(guns = if_else(CC22_330d == 1, guns + 1, guns))

#E: Juevenile/mental health background checks
data <- data %>%
  mutate(guns = if_else(CC22_330e == 1, guns + 1, guns))

#F: Give teachers guns
data <- data %>%
  mutate(guns = if_else(CC22_330f == 2, guns + 1, guns))

data$guns <- data$guns / 6

table(data$guns)
```

### Immigration
```{r}
#Initialize to 0
data$immigration <- 0

#A: Grant legal status if job + taxes for 3+ years
data <- data %>%
  mutate(immigration = if_else(CC22_331a == 1, immigration + 1, immigration))

#B: Increase border patrol agents
data <- data %>%
  mutate(immigration = if_else(CC22_331b == 2, immigration + 1, immigration))

#C: Reduce by 50%
data <- data %>%
  mutate(immigration = if_else(CC22_331c == 2, immigration + 1, immigration))

#D: Increase spending by $25 bil + wall
data <- data %>%
  mutate(immigration = if_else(CC22_331d == 2, immigration + 1, immigration))

data$immigration <- data$immigration / 4
table(data$immigration)
```

### Abortion
```{r}
#Initialize to 0
data$abortion <- 0

#A: Always allow a woman to obtain an abortion
data <- data %>%
  mutate(abortion = if_else(CC22_332a == 1, abortion + 1, abortion))

#B: Permit only in case of rape, incest, danger to mother
data <- data %>%
  mutate(abortion = if_else(CC22_332b == 2, abortion + 1, abortion))

#C: Prohibit after 20th week
data <- data %>%
  mutate(abortion = if_else(CC22_332c == 2, abortion + 1, abortion))

#D: Allow employers to decline coverage
data <- data %>%
  mutate(abortion = if_else(CC22_332d == 2, abortion + 1, abortion))

#E: Prohibit federal funding
data <- data %>%
  mutate(abortion = if_else(CC22_332e == 2, abortion + 1, abortion))

#F: Always illegal
data <- data %>%
  mutate(abortion = if_else(CC22_332f == 2, abortion + 1, abortion))

data$abortion <- data$abortion / 6

table(data$abortion)
```

### Climate
```{r}
#Initialize to 0
data$climate <- 0

# From what you know about global climate change or global warming, which one of
# the following statements comes closest to your opinion?
# 1: Global climate change has been established as a serious problem, and
# immediate action is necessary
# 2: There is enough evidence that climate change is taking place and some action 
# should be taken 
# 3: We don't know enough about global climate change, and more research is 
# necessary before we take any actions
# 4: Concern about global climate change is exaggerated. No action is necessary
# 5:  Global climate change is not occurring; this is not a real issue
data <- data %>%
  mutate(climate = if_else(CC22_333 %in% c(1,2), climate + 1, climate))

# A: Give EPA regulatory power
data <- data %>%
  mutate(climate = if_else(CC22_333a == 1, climate + 1, climate))

# B: Set minimum renewable energy
data <- data %>%
  mutate(climate = if_else(CC22_333b == 1, climate + 1, climate))

# C: Strengthen Clean Energy Act
data <- data %>%
  mutate(climate = if_else(CC22_333c == 1, climate + 1, climate))

# D: Set new fuel efficiency standards
data <- data %>%
  mutate(climate = if_else(CC22_333d == 1, climate + 1, climate))

# E: Increase fossil fuel production
data <- data %>%
  mutate(climate = if_else(CC22_333e == 2, climate + 1, climate))

data$climate <- data$climate / 6

table(data$climate)
```
### Policing
```{r}
#Initialize to 0
data$crime <- 0

#A: Eliminate mandatory minimums
data <- data %>%
  mutate(crime = if_else(CC22_334a == 1, crime + 1, crime))

#B: Require body cams at all times
data <- data %>%
  mutate(crime = if_else(CC22_334b == 1, crime + 1, crime))

#C: Increase police on the street by 10%
data <- data %>%
  mutate(crime = if_else(CC22_334c == 2, crime + 1, crime))

#D: Decrease police on the street by 10%
data <- data %>%
  mutate(crime = if_else(CC22_334d == 1, crime + 1, crime))

#E: Ban chokeholds
data <- data %>%
  mutate(crime = if_else(CC22_334e == 1, crime + 1, crime))

#F: Create bad cop registry
data <- data %>%
  mutate(crime = if_else(CC22_334f == 1, crime + 1, crime))

#G: Stop giving cops surplus weapons
data <- data %>%
  mutate(crime = if_else(CC22_334g == 1, crime + 1, crime))

#H: Allow people to sue police
data <- data %>%
  mutate(crime = if_else(CC22_334h == 1, crime + 1, crime))

data$crime <- data$crime / 8

table(data$crime)
```

### Other Important Demographics
```{r}
data <- data %>%
  # Gender
  mutate(gender = case_when(
    gender4 == 1 ~ "Male",
    gender4 == 2 ~ "Feale",
    gender4 == 3 ~ "Non-binary",
    gender4 == 4 ~ "Other"
  )) %>%
  # Education
  mutate(edu = case_when(
    educ == 1 ~ "No HS",
    educ == 2 ~ "HS grad",
    educ == 3 ~ "Some college",
    educ == 4 ~ "2yr",
    educ == 5 ~ "4yr",
    educ == 6 ~ "Post-grad"
  )) %>%
  # Race
  mutate(race = case_when(
    race == 1 ~ "White",
    race == 2 ~ "Black",
    race == 3 ~ "Hispanic",
    race == 4 ~ "Asian",
    race == 5 ~ "Native American",
    race == 6 ~ "Middle Eastern",
    race == 7 ~ "Multiracial",
    race == 8 ~ "Other"
  )) %>%
  # Party
  mutate(party = case_when(
    pid3 == 1 ~ "Democrat",
    pid3 == 2 ~ "Republican",
    pid3 == 3 ~ "Independent",
    pid3 %in% c(4,5) ~ "Other"
  ))

data <- data %>%
  # Convert presidential approval to binary
  mutate(approval = if_else(CC22_320a %in% c(1,2), 1,0)) %>%
  # Similar for approval of economy
  mutate(economy = case_when(
    CC22_302 %in% c(1,2) ~ 1,
    CC22_302 == 3 ~ 0,
    CC22_302 %in% c(4,5) ~ -1,
  )) %>%
  mutate(voted_D = if_else(presvote20post == 1, 1, 0))
```

### Limit model to relevant columns and only registered voters
```{r}
#colnames(data)
data <- data[data$votereg == 1, 57:68]
summary(lm(voted_D ~ approval + economy + party + edu + gender + health, + guns +
             immigration + abortion + climate + crime,
           data = data))
```

#Create model
##Weigh by issue significance at the time
Find a Gallup poll or something from 2022 to see what people cared about.
Modeling for Dem Vote Share.
TBD exact weighting process.


# Blend with a fundamentals model
Use economy and approval rate. Figure out appropriate weighting

