---
title: "Predictions"
output: html_document
date: "2024-10-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stats)
library(ggplot2)
library(dplyr)
library(lubridate)
library(readr)
```

#NOT DOING THIS NOW, BUT JUST WANTED TO KEEP IN CASE 
```{r}
# SEE ABOVE!!!
#data <- read.csv("~/Desktop/predictions.csv")
#colnames(data)
# file:///Users/andrewcramer/Downloads/31120080_qre.pdf (SEE 314) ((p45-47, 57))
#Q15: Registered voter
#Q19: Senator vote
#Q20: Governor vote
#Q41: Increasing income taxes on people making over one million dollars per years
#Q42: Require background checks for gun purchases at gun shows or other private sales.
#Q49: Increase govt regulation of businesses that produce a great deal of greenhouse emissions linked to climate change
#Q72: Abortion view
#Q74: Concern that immigration poses a threat to the United States
#KS4: Over the past few years, Black Americans have gotten less than they deserve
#Q85 (p69): Highest level of school 
#Q86: Annual income
#Q87: Party
```

# [CES2022 data](https://gdcc.github.io/dataverse-previewers/previewers/v1.4/PDFPreview.html?callback=aHR0cHM6Ly9kYXRhdmVyc2UuaGFydmFyZC5lZHUvYXBpL3YxL2ZpbGVzLzczNTkyNTQvbWV0YWRhdGEvMTAzODA2ODcvdG9vbHBhcmFtcy84MA==&locale=en)

```{r}
data <- read.csv("~/Desktop/CCES22_Common_OUTPUT_vv_small.csv")
#CC22_327grid: Healthcare
#CC22_330grid: Guns
#CC22_331grid: Immigration
#CC22_332grid: Abortion
#CC22_333: Climate
#CC22_333grid: Environment
#CC22_334grid: Policing policies
#pid7

data <- data[, c("gender4", "educ", "race", "votereg", "pid7", 
                 "CC22_327a", "CC22_327b", "CC22_327c", "CC22_327d",
                 "CC22_330a", "CC22_330b", "CC22_330c", "CC22_330d", 
                 "CC22_330e", "CC22_330f", "CC22_331a", "CC22_331b",          
                 "CC22_331c", "CC22_331d", "CC22_332a", "CC22_332b", 
                 "CC22_332c", "CC22_332d", "CC22_332e", "CC22_332f", 
                 "CC22_333", "CC22_333a", "CC22_333b", "CC22_333c",          
                 "CC22_333d", "CC22_333e", "CC22_334a", "CC22_334b", 
                 "CC22_334c", "CC22_334d", "CC22_334e", "CC22_334f", 
                 "CC22_334g", "CC22_334h", "CC22_340a", "CC22_340b",
                 "CC22_340c", "CC22_340d", "CC22_340e", "CC22_340f", 
                 "CC22_340g", "CC22_340h", "CC22_340i", "CC22_340j", 
                 "CC22_340k", "CC22_340l", "CC22_340m", "CC22_340n")]


```
#Clean up dataset
## Create issue scales
Percent of questions on each issue dimension where choose liberal view

###Healthcare
```{r}
# Initialize to 0
data$health <- 0
#A: Expand Medicare
data <- data %>%
  mutate(health = if_else(CC22_327a == 1, health + 1, health))

#B: Government negotiate lower prices
data <- data %>%
  mutate(health = if_else(CC22_327b == 1, health + 1, health))

#C: Repeal Obamacare
data <- data %>%
  mutate(health = if_else(CC22_327c == 2, health + 1, health))

#D: Import prescriptions
data <- data %>%
  mutate(health = if_else(CC22_327d == 1, health + 1, health))

#Average
data$health <- data$health / 4.0

table(data$health)
```
###Gun control
```{r}
# Initialize to 0
data$guns <- 0
#A: Prohibit state from publishing gun registry
data <- data %>%
  mutate(guns = if_else(CC22_330a == 2, guns + 1, guns))

#B: Ban assault rifles
data <- data %>%
  mutate(guns = if_else(CC22_330b == 1, guns + 1, guns))

#C: Easier to obtain concealed-carry permit
data <- data %>%
  mutate(guns = if_else(CC22_330c == 2, guns + 1, guns))

#D: Funding to encourage states to take guns away from self-threats
data <- data %>%
  mutate(guns = if_else(CC22_330d == 1, guns + 1, guns))

#E: Juevenile/mental health background checks
data <- data %>%
  mutate(guns = if_else(CC22_330e == 1, guns + 1, guns))

#F: Give teachers guns
data <- data %>%
  mutate(guns = if_else(CC22_330f == 2, guns + 1, guns))

data$guns <- data$guns / 6

table(data$guns)
```

###Immigration
```{r}
#Initialize to 0
data$immigration <- 0

#A: Grant legal status if job + taxes for 3+ years
data <- data %>%
  mutate(immigration = if_else(CC22_331a == 1, immigration + 1, immigration))

#B: Increase border patrol agents
data <- data %>%
  mutate(immigration = if_else(CC22_331b == 2, immigration + 1, immigration))

#C: Reduce by 50%
data <- data %>%
  mutate(immigration = if_else(CC22_331c == 2, immigration + 1, immigration))

#D: Increase spending by $25 bil + wall
data <- data %>%
  mutate(immigration = if_else(CC22_331d == 2, immigration + 1, immigration))

data$immigration <- data$immigration / 4
table(data$immigration)
```

#Create model
##Weigh by issue significance at the time
Find a Gallup poll or something from 2022 to see what people cared about.
Modeling for Dem Vote Share.
TBD exact weighting process.


# Blend with a fundamentals model
Use economy and approval rate. Figure out appropriate weighting

